\section{Meeting~\arabic{section}: March 1, 2017}
\subsection*{Present at meeting}
Samuel Gauthier, Loïc Charrière, Claude Fuhrer
\subsection*{Agenda}
\begin{itemize}
	\item Present  the Use Cases  and User stories
	\item Discussion about the usage of Python
\end{itemize}
\subsection*{Notes}
	\subsubsection{Use Cases and User stories}
	\begin{itemize}
        	\item Vision\&Goals: The vision and goals of the project have to be enhanced and not taken ``as is''.
		\item If a choice is made during the project, we should write down why it has been made this way. Everything that hasn't been documented is considered not been done.
		\item If we go for a specific product (such as DBMS, module, etc.) we should at least try out other alternatives (2--3) and explain why we made the choice of using this specific product.
		\item Split the user story ``reate/delete categories'' in two.
		\item Sort the uses cases by topic.
		\item Alarms could be snoozed. (for example, if the user is at a meeting snooze all alarms so that they don't disturb the meeting) 
		\item Alarms should be user specific, i.e., they should belong to the user connected on the computer and not be shared across all the users of the machine.
		\item Book recommendation (chapter about use cases) -> Applying UML and Patterns (Larman).
	\end{itemize}
	\subsubsection{Usage of Python}
	\begin{itemize}
		\item Strongly discouraged to share python code via e-mail (General life advice)
		\item Code coverage 70--80\% is ok, 30\% is not
        \end{itemize}
\subsection*{Tasks}
	\begin{itemize}
		\item Improve vision\&goals
		\item Create use cases / user stories / actors correctly
		\item Read Python doc
	\end{itemize}
\subsection*{Next Meeting}
\st{TBD} (edit)
March 17, 2017
