\section{Meeting~\arabic{section}: March 17, 2017}
\subsection*{Present at meeting}
Samuel Gauthier, Loïc Charrière, Claude Fuhrer
\subsection*{Agenda}
\begin{itemize}
    \item System and Context Boundaries
    \item System diagrams
    \item System description
\end{itemize}
\subsection*{Notes}
    The Project Goals should not be written down as a list. We need to create
    full sentences in order to help the reader's comprehension.\\
    \textbf{Question:} ``Should this document contain snippets of code?''\\
    \textbf{Answer:} It depends on the target audience. But here we should
    only show snippets of pseudo code for complicated parts of our code.
    \subsubsection{System and Context Boundaries}
    \begin{itemize}
        \item Some of the Stakeholders will not influence our project. They
            are only there so that our documentation is complete.
    \end{itemize}
    \subsubsection*{System diagrams}
    \begin{itemize}
        \item Good domain model.
        \item The domain model should contain types only if they
            are very specific and part of the DM\@.
        \item It is not useful to specify interfaces and abstract classes.
    \end{itemize}
    \subsubsection*{System description}
    \begin{itemize}
        \item We need to link the User Stories and Use Cases.
    \end{itemize}
    \subsection*{Other}
    \textbf{Question:} ``How should our workflow be? Should we write the
    documentation and the code at the same time?''\\
    \textbf{Answer:} We shouldn't waste too much time on writing documentation.
    Basically we should use the Scrum method. All the Use Cases (or the most
    important ones) have to be written down. Then we can decide what has to
    be included in each sprints. For each sprint we must have a working version
    of our application. Start with a small version having the alerts date
    hard coded in the code, with no GUI.\@ Then add a new feature with each
    sprints.
\subsection*{Tasks}
    \begin{itemize}
        \item Rewrite the Project Goals
        \item Prepare sprints
    \end{itemize}
\subsection*{Next Meeting}
TBD
